---
title: "KEY WORDS - Nini"
output: html_document
date: "2025-04-13"
---

```{r}

#install.packages("readtext")
library(quanteda)
library(readtext)
library(tidyverse)


```


```{r}

kh_articles <- read.csv("kharris_extracted_text_jan2025.csv")

kh_articles <- kh_articles %>%
  mutate(filename = paste0(filename, "_", row_number()))

```


```{r}

# Create a corpus using the 'sentence' column as the text field
kh_corpus <- corpus(kh_articles, text_field = "sentence", docid_field = "filename") # build a new corpus from the texts
head(kh_corpus)

```


```{r}

# Tokenize the corpus
kh_tokens <- tokens(kh_corpus)

# Perform KWIC (Key Word in Context) search on the tokens
kh_quanteda_test <- kwic(kh_tokens, pattern = "kamala", valuetype = "regex") %>% 
  as.data.frame()

kh_quanteda_test2 <- kwic(kh_tokens, phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")), window = 50, valuetype = "regex") %>% as.data.frame() 

#write.csv(quanteda_test, "quanteda_test.csv")

```


```{r}

#I know it is the same as the one above, just wanted try differently

kh_kwic_results <- kwic(
  kh_tokens,
  phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")),
  window = 50, valuetype = "regex"
) %>% 
  as.data.frame() 


```



```{r}

kh_kwic_results <- kh_kwic_results |>
  mutate(matchrow = docname)



```

```{r}
#Strips out unique file name from article index 
kh_kwic_results <- kh_kwic_results |>  
    mutate(matchrow = str_extract(docname, "^[^_]+_[^_]+"))

kh_metadata <- kh_articles

# Join KWIC results with metadata 
kh_kwic_with_metadata <- kh_kwic_results %>%
  inner_join(kh_articles, by = c("docname" = "filename")) %>% 
  distinct(docname, .keep_all = TRUE) %>% 
  select(docname, from, to, pre, keyword, post, pattern)


```

The only thing I did not understand how to do was how to apply these housecleaning codes to this case


# Housecleaning

#cut useless returns
kh_mobjunk <- c("")
kh_kwic_with_metadata <- kh_kwic_with_metadata %>%
  filter(!keyword %in% kh_mobjunk)


#Eliminate duplication
kh_kwic_with_metadata  <- kh_kwic_with_metadata  %>% 
  distinct(docname, pre, keyword, post, newspaper_name, date, url) %>% 
  rename('Beginning of Passage' = pre, 'End of Passage' = post, Newspaper = newspaper_name, Date = date) 

kwic_with_metadata_csv <- kwic_with_metadata  %>%
  add_column(Code = NA) %>% 
  add_column(Comments = NA) %>% 
  select(docname, Newspaper, Date, 'Beginning of Passage', keyword, 'End of Passage', Code, Comments)



Donald Trump

```{r}

dt_articles <- read.csv("trump_extracted_text_jan2025.csv")

dt_articles <- dt_articles %>%
  mutate(filename = paste0(filename, "_", row_number()))

```


```{r}

# Create a corpus using the 'sentence' column as the text field
dt_corpus <- corpus(dt_articles, text_field = "sentence", docid_field = "filename") # build a new corpus from the texts
head(dt_corpus)

```


```{r}

# Tokenize the corpus
dt_tokens <- tokens(dt_corpus)

# Perform KWIC (Key Word in Context) search on the tokens
dt_quanteda_test <- kwic(dt_tokens, pattern = "donald", valuetype = "regex") %>% 
  as.data.frame()

dt_quanteda_test2 <- kwic(dt_tokens, phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")), window = 50, valuetype = "regex") %>% as.data.frame() 

#write.csv(quanteda_test, "quanteda_test.csv")

```


```{r}

#I know it is the same as the one above, just wanted try differently

dt_kwic_results <- kwic(
  dt_tokens,
  phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")),
  window = 50, valuetype = "regex"
) %>% 
  as.data.frame() 


```



```{r}

dt_kwic_results <- dt_kwic_results |>
  mutate(matchrow = docname)



```

```{r}
#Strips out unique file name from article index 
dt_kwic_results <- dt_kwic_results |>  
    mutate(matchrow = str_extract(docname, "^[^_]+_[^_]+"))

dt_metadata <- dt_articles

# Join KWIC results with metadata 
dt_kwic_with_metadata <- dt_kwic_results %>%
  inner_join(dt_articles, by = c("docname" = "filename")) %>% 
  distinct(docname, .keep_all = TRUE) %>% 
  select(docname, from, to, pre, keyword, post, pattern)


```