---
title: "KEY WORDS - Nini"
output: html_document
date: "2025-04-13"
---

```{r}

#install.packages("readtext")
library(quanteda)
library(readtext)
library(tidyverse)


```


```{r}

kh_articles <- read.csv("../kharris_extracted_text_jan2025.csv")

kh_articles <- kh_articles %>%
  mutate(filename = paste0(filename, "_", row_number()))

```


```{r}

# Create a corpus using the 'sentence' column as the text field
kh_corpus <- corpus(kh_articles, text_field = "sentence", docid_field = "filename") # build a new corpus from the texts
head(kh_corpus)

```


```{r}

# Tokenize the corpus
kh_tokens <- tokens(kh_corpus)

# Perform KWIC (Key Word in Context) search on the tokens
kh_quanteda_test <- kwic(kh_tokens, pattern = "kamala", valuetype = "regex") %>% 
  as.data.frame()

kh_kwic_results <- kwic(kh_tokens, phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "\\btrans\\b")), window = 50, valuetype = "regex") %>% as.data.frame() 

#write.csv(quanteda_test, "quanteda_test.csv")

```



```{r}

kh_kwic_results <- kh_kwic_results |>
  mutate(matchrow = docname)



```

```{r}
#Strips out unique file name from article index 
kh_kwic_results <- kh_kwic_results |>  
    mutate(matchrow = str_extract(docname, "^[^_]+_[^_]+"))

kh_metadata <- kh_articles

# Join KWIC results with metadata 
kh_kwic_with_metadata <- kh_kwic_results %>%
  inner_join(kh_articles, by = c("docname" = "filename")) %>% 
  distinct(docname, .keep_all = TRUE) %>% 
  select(docname, from, to, pre, keyword, post, pattern)


```

# Housecleaning

Example from Marilyn
clean_df <- articles_df %>%
  mutate(text = str_squish(sentence)) %>% #gets rid of leading and trailing spaces + double spaces
  mutate(text = tolower(text)) %>%
  mutate(text = str_replace(text, "startofarticle", "")) %>%
  mutate(text = str_replace_all(text, "__", "")) %>%
  mutate(text = gsub("issn:\\s+\\S+", "", text)) %>%
  mutate(text = gsub("http[^ ]*", "http", text)) %>%
  mutate(text = str_replace_all(text, c(
    "copyright" = "",
    "database: proquest central" = "",
    "language of publication: english" = "",
    "document url:\\s+\\S+" = "",
    "proquest document id:\\s+\\S+" = "",
    "publication subject:\\s+\\S+" = "",
    "publication date:\\s+\\S+" = "",
    "publication-type:\\s+\\S+" = "",
    "pages:\\s+\\S+" = "",
    "publication info" = "",
    "last updated:\\s+\\S+" = "",
    "interest periodicals--united states" = "",
    "all rights resesrved" = "",
    "load-date" = "",
    "all rights reserved" = "", 
    "new york times" = "",
    "language: english" = "",
    "author:\\s+\\S+" = "",
    "abstract:\\s+\\S+" = "",
    "links:\\s+\\S+" = "",
    "publication title:\\s+\\S+" = "",
    "volume:\\s+\\S+" = "",
    "issue:\\s+\\S+" = "",
    "publication year:\\s+\\S+" = "",
    "publisher: windy city media group" = "",
    "place of publication: chicago, ill." = "",
    "country of publication: united states, chicago, ill." = "",
    "document type:\\s+\\S+" = "",
    "database: genderwatch" = "",
    "identifier / keyword: y; genderwatch" = "",
    "source type: newspaper" = "",
    "windy city times" = "",
    "umcp.primo.exlibrisgroup.com\\s+\\S+" = "",
    "usmai-umcp.primo.exlibrisgroup.com" = "",
    "id doi" = "",
    "Links: https://usmai-umcp.primo.exlibrisgroup.com/" = "",
    "windy city media group" = "",
    "city times; chicago, ill." = "",
    "http" = "",
    "document feature:\\s+\\S+" = "",
    "feature photographs" = "",
    "full text:" = "",
    "city times" = "",
    "subject:\\s+\\S+" = "",
    "company / organization:\\s+\\S+" = "",
    "location:\\s+\\S+" = "",
    "illinois; united states--us; illinois" = "",
    "business indexing term:" = "",
    "ch icago, ill." = "",
    "title" = "", 
    "web site:\\s+\\S+" = ""
  ))) 





```{r}


#cut useless returns
kh_mobjunk <- c("http", "mt", "rt", "@KamalaHarris")
kh_kwic_with_metadata <- kh_kwic_with_metadata %>%
  filter(!keyword %in% kh_mobjunk)
```

```{r}
#Eliminate duplication
kh_kwic_with_metadata  <- kh_kwic_with_metadata  %>% 
  distinct(docname, pre, keyword, post, pattern) %>% 
  rename('Beginning of Passage' = pre, 'End of Passage' = post) 

```

Donald Trump

```{r}

dt_articles <- read.csv("../trump_extracted_text_jan2025.csv")

dt_articles <- dt_articles %>%
  mutate(filename = paste0(filename, "_", row_number()))

```


```{r}

# Create a corpus using the 'sentence' column as the text field
dt_corpus <- corpus(dt_articles, text_field = "sentence", docid_field = "filename") # build a new corpus from the texts
head(dt_corpus)

```


```{r}

# Tokenize the corpus
dt_tokens <- tokens(dt_corpus)

# Perform KWIC (Key Word in Context) search on the tokens
dt_quanteda_test <- kwic(dt_tokens, pattern = "donald", valuetype = "regex") %>% 
  as.data.frame()

dt_quanteda_test2 <- kwic(dt_tokens, phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")), window = 50, valuetype = "regex") %>% as.data.frame() 

#write.csv(quanteda_test, "quanteda_test.csv")

```


```{r}

#I know it is the same as the one above, just wanted try differently

dt_kwic_results <- kwic(
  dt_tokens,
  phrase(c("kamala", "harris", "donald", "trump", "immigration", "immigrant", "black", "men", "trans")),
  window = 50, valuetype = "regex"
) %>% 
  as.data.frame() 


```



```{r}

dt_kwic_results <- dt_kwic_results |>
  mutate(matchrow = docname)



```

```{r}
#Strips out unique file name from article index 
dt_kwic_results <- dt_kwic_results |>  
    mutate(matchrow = str_extract(docname, "^[^_]+_[^_]+"))

dt_metadata <- dt_articles

# Join KWIC results with metadata 
dt_kwic_with_metadata <- dt_kwic_results %>%
  inner_join(dt_articles, by = c("docname" = "filename")) %>% 
  distinct(docname, .keep_all = TRUE) %>% 
  select(docname, from, to, pre, keyword, post, pattern)


```