---
title: "Daily Wire Scraper"
author: "Wells"
date: "04-15-2025"
  output:
  html_document: default
  pdf_document: default
---

```{r}
# Install and load required packages if not already installed
#install.packages("rvest")
library(rvest)
library(tidyverse)
library(jsonlite)
library(httr)
#install.packages("googleAuthR")
library(googleAuthR)
library(lubridate)
```

```{r}
# Install and load required packages


# Set up API credentials
# You'll need to get these from Google Cloud Console
# Visit: https://console.cloud.google.com/
# 1. Create a project
# 2. Enable Custom Search API
# 3. Create credentials
# 4. Set up a Custom Search Engine at https://programmablesearchengine.google.com/

#umd.edu- https://programmablesearchengine.google.com/controlpanel/overview?cx=44897a96926a84be3
```

# Important! DO NOT STORE YOUR API Key in GitHub!

```{r echo=FALSE}

Sys.setenv(GOOGLE_SEARCH_API_KEY = "XXXXX")
Sys.setenv(GOOGLE_SEARCH_ENGINE_ID = "XXXXX")


```

# Your credentials here
System environment variables exist at the operating system level, providing a more secure way to store sensitive information like API keys. They won't appear in your normal R environment but remain accessible across different sessions. You retrieve them using Sys.getenv(). These credentials typically persist only for the duration of your current R session.
```{r}

api_key <- Sys.getenv("GOOGLE_SEARCH_API_KEY")
search_engine_id  <- Sys.getenv("GOOGLE_SEARCH_ENGINE_ID")

```

# Extract articles by date
```{r}
# Function to search using Google Custom Search API with pagination
google_search_all <- function(api_key, search_engine_id) {
  base_url <- "https://www.googleapis.com/customsearch/v1"
  all_results <- data.frame(
    url = character(),
    title = character(),
    snippet = character(),
    stringsAsFactors = FALSE
  )
  
  # The exact search query
  #Change the dates here
  full_query <- 'site:www.dailywire.com "kamala harris" after:2024-08-01 before:2024-08-10'
  
  # Google only allows up to 100 pages 
  for(start_index in seq(1, 300, 10)) {
    # Add delay to avoid hitting rate limits
    Sys.sleep(1)
    
    response <- GET(
      base_url,
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = full_query,
        start = start_index
      )
    )
    
    results <- fromJSON(rawToChar(response$content))
    
    # Check if we have items in the response
    if(!is.null(results$items)) {
      page_df <- data.frame(
        url = results$items$link,
        title = results$items$title,
        snippet = results$items$snippet,
        stringsAsFactors = FALSE
      )
      
      all_results <- rbind(all_results, page_df)
      
      # Print progress
      cat("Retrieved results", start_index, "to", start_index + nrow(page_df) - 1, "\n")
    } else {
      # If no more results, break the loop
      break
    }
  }
  
  return(all_results)
}


# Get all results
all_urls_df <- google_search_all(api_key, search_engine_id)

# Remove any duplicates
august_10_urls_df <- unique(all_urls_df)

# Print total number of results
cat("\nTotal unique articles found:", nrow(all_urls_df), "\n")

# Save to CSV
#write.csv(sept_urls_df, "sept_kamala_harris_all_articles.csv", row.names = FALSE)
```
#determine search results per month

```{r}


# Function to count search results by date
count_results_by_date <- function(api_key, search_engine_id, site, search_term, date_ranges) {
 #creates empty dataframe that stores search result counts
   results_count <- data.frame(
    date_range = character(),
    result_count = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (date_range in date_ranges) {
    # Building the search query
    query <- paste0('site:', site, ' "', search_term, '" after:', date_range[1], ' before:', date_range[2])
    
    # Make the API request
    response <- GET(
      "https://www.googleapis.com/customsearch/v1",
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = query,
        num = 1  # requests only 1 result -only need the count, not actual results
      )
    )
    
    # Parse the response
    # Checks if the API request was successful (status code 200)
    if (status_code(response) == 200) {
      results <- fromJSON(rawToChar(response$content))
      
      # Extracts the total result count 
      total_results <- as.numeric(results$searchInformation$totalResults)
      
      # Add to dataframe
      new_row <- data.frame(
        date_range = paste(date_range[1], "to", date_range[2]),
        result_count = total_results,
        stringsAsFactors = FALSE
      )
      
      results_count <- rbind(results_count, new_row)
      
      message("Query: ", query)
      message("Results: ", total_results)
    } else {
      message("Error for date range ", date_range[1], " to ", date_range[2], 
              ": Status code ", status_code(response))
    }
    
    # One second pause to avoid hitting rate limits with API query
    Sys.sleep(1.5)
  }
  #Returns the completed data frame containing all date ranges and their corresponding result counts
  return(results_count)
}

# Define your parameters
site <- "www.dailywire.com"
search_term <- "kamala harris"

# Define date ranges to check (monthly intervals)
date_ranges <- list(
  c("2024-07-01", "2024-07-31"),
  c("2024-08-01", "2024-08-31"),
  c("2024-09-01", "2024-09-30"),
  c("2024-10-01", "2024-10-31"),
  c("2024-11-01", "2024-11-05")
)

# If you want to see how results are distributed within September
# september_ranges <- list(
#   c("2024-09-01", "2024-09-10"),
#   c("2024-09-11", "2024-09-20"),
#   c("2024-09-21", "2024-09-30")
# )

# If you want to see how results are distributed within a month

# august_ranges <- list(
#   c("2024-08-01", "2024-08-15"),
#   c("2024-08-16", "2024-08-31")
# )

# october_ranges <- list(
#   c("2024-10-01", "2024-10-10"),
#   c("2024-10-11", "2024-10-20"),
#   c("2024-10-21", "2024-10-31")
# )

```

# Run the function, count monthly data
```{r}
monthly_counts <- count_results_by_date(api_key, search_engine_id, site, search_term, date_ranges)
# View results
print(monthly_counts)
```

```{r}
# # Create a simple bar chart of monthly results
barplot(monthly_counts$result_count,
        names.arg = monthly_counts$date_range,
        main = "DailyWire Articles Mentioning 'Kamala Harris' by Month",
        xlab = "Month",
        ylab = "Number of Articles",
        col = "steelblue",
        family = "sans")  # Using 'sans' as a default font family that should be available
```



```{r}
# Run the count for monthly segments
august_counts <- count_results_by_date(api_key, search_engine_id, site, search_term, august_ranges)
print(august_counts)

#For other months,

#october_counts <- count_results_by_date(api_key, search_engine_id, site, search_term, october_ranges)

```

#-------------------------------------------------------------------------------
# Part 2 : Scraping the text
#-------------------------------------------------------------------------------


#I asked ChatGPT:  build a webscraper this into a function so it will extract URLs from Daily_Wire_Articles.xlsx from the URL column and produce one text file per article. there are 20 URLs on that list.

```{r}


# Define the function to scrape a Daily Wire article
scrape_article <- function(url) {
  # Read the HTML content of the page
  page <- tryCatch(
    read_html(url),
    error = function(e) {
      message(paste("Error reading:", url))
      return(NULL)
    }
  )
  
  # Return NULL if page could not be loaded
  if (is.null(page)) return(NULL)

  # Extract the headline (assuming it's in an <h1> tag)
  headline <- page %>%
    html_element("h1") %>%
    html_text(trim = TRUE)

  # Extract the article text (all <p> elements)
  article_text <- page %>%
    html_elements("p") %>%
    html_text(trim = TRUE) %>%
    paste(collapse = "\n")

  # Combine headline and article into one string
  full_text <- paste("Headline:\n", headline, "\n\nArticle Text:\n", article_text)
  
  return(full_text)
}

# Read the URLs from the Excel file
# You will need to point to the location of your Daily Wire Articles spreadsheet.
# urls <- read_excel("~/Code/CompText_Jour/data/Daily_Wire_Articles.xlsx", sheet = 1)$URL

urls <- august_10_urls_df$url
# Create directory if it doesn't exist
dir.create("extracted_articles", showWarnings = FALSE)

# Loop over URLs and save each article as a text file
for (url in urls) {
  article_content <- scrape_article(url)
  
  # Skip if article content is NULL
  if (is.null(article_content)) next
  
  # Create a filename from the URL (using only the last part)
  filename <- paste0(basename(url), ".txt")
  
  # Create the full path including the new directory
  filepath <- file.path("extracted_articles", filename)
  
  # Save the article content to a text file in the new directory
  writeLines(article_content, con = filepath)
  
  message(paste("Saved:", filepath))
}

```

#Create a final index

```{r}
#add the url_df here
final_index <- rbind(august_10_urls_df, sept_urls_df) |> 
  # Extract date pattern from snippet column
  mutate(date_str = str_extract(snippet, "[A-Z][a-z]{2}\\s+\\d{1,2},\\s+\\d{4}")) %>%
  # Convert extracted strings to Date objects
  mutate(date = mdy(date_str)) %>%
  # Remove the intermediate string column if you don't need it
  select(-date_str)


write.csv(final_index, "daily_wire_extracted_articles.csv")
```

