---
title: "Daily Wire Scraper"
author: "Rob Wells and his pal Claude.ai"
date: "05-07-2025"
  output:
  html_document: default
  pdf_document: default
---

This notebook runs a Google power search query on a specific news site and then scrapes the results into individual text files into a separate folder. It compiles an index of the results with headline, date and URL.

It uses the Google Search API which is a rough way to extract article text from a website without the API access.

There are important limitations:

Google Search API limits results to 100 specific URLs at a time. 

For researchers seeking to several hundred or several thousand results, you can get around that by determining the result distribution and then breaking up the searches into blocks of 100 and compiling the results.

The first step is to use Google power search operators to find your material and validate the search results. We did this to get all Kamala Harris articles on the Daily Wire:

site:www.dailywire.com "kamala harris" after:2024-08-01 before:2024-08-10

Special thanks Nino Mtchedlisvili for her assistance on this project.


```{r}
# Install and load required packages if not already installed
#install.packages("rvest")
library(rvest)
library(tidyverse)
library(jsonlite)
library(httr)
#install.packages("googleAuthR")
library(googleAuthR)
library(lubridate)
```


# Set up API credentials
```{r}
# You'll need to get these from Google Cloud Console
# Visit: https://console.cloud.google.com/
# 1. Create a project
# 2. Enable Custom Search API
# 3. Create credentials
# 4. Set up a Custom Search Engine at https://programmablesearchengine.google.com/
```

# Important! DO NOT STORE YOUR API Key in GitHub!

```{r echo=FALSE}

Sys.setenv(GOOGLE_SEARCH_API_KEY = "XXX")
Sys.setenv(GOOGLE_SEARCH_ENGINE_ID = "XXXX")


```

# Your credentials here
System environment variables exist at the operating system level, providing a more secure way to store sensitive information like API keys. They won't appear in your normal R environment but remain accessible across different sessions. You retrieve them using Sys.getenv(). These credentials typically persist only for the duration of your current R session.
```{r}

api_key <- Sys.getenv("GOOGLE_SEARCH_API_KEY")
search_engine_id  <- Sys.getenv("GOOGLE_SEARCH_ENGINE_ID")

```

# Count search results by date
### Define your search parameters
```{r}
# Define your parameters
site <- "www.dailywire.com"
search_term <- "kamala harris"

# Define date ranges to check (monthly intervals)
date_ranges <- list(
  c("2024-07-01", "2024-07-31"),
  c("2024-08-01", "2024-08-31"),
  c("2024-09-01", "2024-09-30"),
  c("2024-10-01", "2024-10-31"),
  c("2024-11-01", "2024-11-05")
)

# If you want to see how results are distributed within September
# september_ranges <- list(
#   c("2024-09-01", "2024-09-10"),
#   c("2024-09-11", "2024-09-20"),
#   c("2024-09-21", "2024-09-30")
# )

```


# Count search results by month
New version specifies Google search in the US, use English and disables personalization of search results. All done for consistent results.
Counting function is new (5-7-2025)
```{r}
count_results_by_date <- function(api_key, search_engine_id, site, search_term, date_ranges, max_pages = 10) {
  # Creates empty dataframe that stores search result counts
  results_count <- data.frame(
    date_range = character(),
    estimated_count = numeric(),
    actual_count = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (date_range in date_ranges) {
    # Building the search query
    query <- paste0('site:', site, ' "', search_term, '" after:', date_range[1], ' before:', date_range[2])
    
    # Initialize variables
    estimated_results <- 0
    actual_total_results <- 0
    page_count <- 0
    has_more_results <- TRUE
    
    # We'll use this to track which URLs we've seen
    all_links <- character(0)
    
    while (has_more_results && page_count < max_pages) {
      # Calculate the start index - Google API uses 1-based indexing
      start_index <- page_count * 10 + 1
      
      message("Fetching page with start index: ", start_index)
      
      # Make API request
      tryCatch({
        response <- GET(
          "https://www.googleapis.com/customsearch/v1",
          query = list(
            key = api_key,
            cx = search_engine_id,
            q = query,
            num = 10,
            start = start_index,
            personalization = "false",
            gl = "us",
            hl = "en"
          )
        )
        
        # Check if response was successful
        if (status_code(response) == 200) {
          # Convert response to text first for easier debugging if needed
          response_text <- rawToChar(response$content)
          
          # Parse the response as JSON
          parsed <- fromJSON(response_text)
          
          # Debug output - really see what we're getting
          message("Response successfully parsed")
          
          # Get the estimated total count from the first page
          if (page_count == 0 && !is.null(parsed$searchInformation$totalResults)) {
            estimated_results <- as.numeric(parsed$searchInformation$totalResults)
            message("Estimated total results: ", estimated_results)
          }
          
          # Now let's try to access the items directly using str() to examine its structure
          if (!is.null(parsed$items)) {
            # Convert to character to extract links with regex
            response_str <- response_text
            
            # Use regex to extract links - look for "link": "http... pattern
            links <- gregexpr('"link":\\s*"([^"]+)"', response_str, perl = TRUE)
            link_matches <- regmatches(response_str, links)
            
            if (length(link_matches) > 0 && length(link_matches[[1]]) > 0) {
              # Extract just the URLs from the matches
              extracted_links <- gsub('"link":\\s*"', "", link_matches[[1]])
              extracted_links <- gsub('"', "", extracted_links)
              
              message("Found ", length(extracted_links), " links on this page")
              
              # Add these links to our collection if they're new
              for (link in extracted_links) {
                if (!(link %in% all_links)) {
                  all_links <- c(all_links, link)
                }
              }
            } else {
              message("No links found on this page")
            }
            
            # Increment page count
            page_count <- page_count + 1
            
            # Check if we got a full page of results (10 items)
            # If not, we've reached the end
            if (is.null(parsed$items) || length(link_matches[[1]]) < 10) {
              has_more_results <- FALSE
              message("Less than 10 results on page, must be the end")
            }
          } else {
            message("No items found in response")
            has_more_results <- FALSE
          }
        } else {
          message("Error: Status code ", status_code(response))
          has_more_results <- FALSE
        }
      }, error = function(e) {
        message("Error processing response: ", conditionMessage(e))
        has_more_results <- FALSE
      })
      
      # Avoid hitting rate limits
      Sys.sleep(1.5)
    }
    
    # After processing all pages, get unique count
    actual_total_results <- length(all_links)
    
    # Add results to dataframe
    new_row <- data.frame(
      date_range = paste(date_range[1], "to", date_range[2]),
      estimated_count = estimated_results,
      actual_count = actual_total_results,
      stringsAsFactors = FALSE
    )
    
    results_count <- rbind(results_count, new_row)
    
    # Final message for this date range
    message("Final results for date range: ", date_range[1], " to ", date_range[2])
    message("Estimated results: ", estimated_results)
    message("Actual unique URLs found: ", actual_total_results)
    message("Pages checked: ", page_count)
    
    # Optional: List all the unique URLs found 
    if (actual_total_results > 0) {
      message("All unique URLs found:")
      for (i in 1:length(all_links)) {
        message(i, ". ", all_links[i])
      }
    }
    
    message("------------------------------------")
    
    # Pause before next date range
    Sys.sleep(1.5)
  }
  
  return(results_count)
}

```




# Run the function, count monthly data
```{r}
monthly_counts <- count_results_by_date(api_key, search_engine_id, site, search_term, date_ranges)
# View results
print(monthly_counts)
```



# Graph monthly results

```{r}
library(ggplot2)
monthly_counts |> 
  mutate(month = case_when(
    str_detect(date_range, "2024-07-01") ~ "July",
    str_detect(date_range, "2024-08-01") ~ "Aug",
    str_detect(date_range, "2024-09-01") ~ "Sept",
    str_detect(date_range, "2024-10-01") ~ "Oct",
    str_detect(date_range, "2024-11-01") ~ "Nov",
    TRUE ~ date_range  # Default case to handle any unmatched values
  )) |> 
  mutate(month = factor(month, levels = c("July", "Aug", "Sept", "Oct", "Nov"))) |>
ggplot(aes(x = month, y = result_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(
    title = "DailyWire Articles Mentioning 'Kamala Harris' by Month",
    x = "Month",
    y = "Number of Articles"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    text = element_text(family = "sans"),
    plot.title = element_text(hjust = 0.5)
  )
```

# Query to fetch article URLs by date

### Specify search query parameters
```{r}
site <- "www.dailywire.com"
search_term <- "kamala harris"
#Dates
date_after <- "2024-08-01"
date_before <- "2024-08-31"
```


# Search query to extract the URLS

```{r}
google_search_all <- function(api_key, search_engine_id) {
  base_url <- "https://www.googleapis.com/customsearch/v1"
  all_results <- data.frame(
    url = character(),
    title = character(),
    snippet = character(),
    stringsAsFactors = FALSE
  )
  

  
  # Google only allows up to 100 pages 
  for(start_index in seq(1, 300, 10)) {
     # Building the search query
    query <- paste0('site:', site, ' "', search_term, '" after:', date_after, ' before:', date_before)
    
    # Add delay to avoid hitting rate limits
    Sys.sleep(1)
    
    response <- GET(
      base_url,
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = query,
        start = start_index,
        personalization = "false",  # Disable personalization
        gl = "us",                  # Set country to US
        hl = "en"                   # Set language to English
      )
    )
    
    results <- fromJSON(rawToChar(response$content))
    
    # Check if we have items in the response
    if(!is.null(results$items)) {
      page_df <- data.frame(
        url = results$items$link,
        title = results$items$title,
        snippet = results$items$snippet,
        stringsAsFactors = FALSE
      )
      
      all_results <- rbind(all_results, page_df)
      
      # Print progress
      cat("Retrieved results", start_index, "to", start_index + nrow(page_df) - 1, "\n")
    } else {
      # If no more results, break the loop
      break
    }
  }
  
  return(all_results)
}

# Get all results
all_urls_df <- google_search_all(api_key, search_engine_id)
# Remove any duplicates
clean_urls_df <- unique(all_urls_df)
# Print total number of results
cat("\nTotal unique articles found:", nrow(clean_urls_df), "\n")
```


#-------------------------------------------------------------------------------
# Part 2 : Scraping the text
#-------------------------------------------------------------------------------


#I asked ChatGPT:  build a webscraper this into a function so it will extract URLs from Daily_Wire_Articles.xlsx from the URL column and produce one text file per article. there are 20 URLs on that list.

```{r}
# Define the function to scrape a Daily Wire article
scrape_article <- function(url) {
  # Read the HTML content of the page
  page <- tryCatch(
    read_html(url),
    error = function(e) {
      message(paste("Error reading:", url))
      return(NULL)
    }
  )
  
  # Return NULL if page could not be loaded
  if (is.null(page)) return(NULL)

  # Extract the headline (assuming it's in an <h1> tag)
  headline <- page %>%
    html_element("h1") %>%
    html_text(trim = TRUE)

  # Extract the article text (all <p> elements)
  article_text <- page %>%
    html_elements("p") %>%
    html_text(trim = TRUE) %>%
    paste(collapse = "\n")

  # Combine headline and article into one string
  full_text <- paste("Headline:\n", headline, "\n\nArticle Text:\n", article_text)
  
  return(full_text)
}

# Read the URLs from the Excel file
# You will need to point to the location of your Daily Wire Articles spreadsheet.
# urls <- read_excel("~/Code/CompText_Jour/data/Daily_Wire_Articles.xlsx", sheet = 1)$URL

urls <- clean_urls_df$url
# Create directory if it doesn't exist
dir.create("extracted_articles", showWarnings = FALSE)

# Loop over URLs and save each article as a text file
for (url in urls) {
  article_content <- scrape_article(url)
  
  # Skip if article content is NULL
  if (is.null(article_content)) next
  
  # Create a filename from the URL (using only the last part)
  filename <- paste0(basename(url), ".txt")
  
  # Create the full path including the new directory
  filepath <- file.path("extracted_articles", filename)
  
  # Save the article content to a text file in the new directory
  writeLines(article_content, con = filepath)
  
  message(paste("Saved:", filepath))
}

```

#Create a final index

```{r}
#add the url_df here
final_index <- rbind(august_10_urls_df, sept_urls_df) |> 
  # Extract date pattern from snippet column
  mutate(date_str = str_extract(snippet, "[A-Z][a-z]{2}\\s+\\d{1,2},\\s+\\d{4}")) %>%
  # Convert extracted strings to Date objects
  mutate(date = mdy(date_str)) %>%
  # Remove the intermediate string column if you don't need it
  select(-date_str)


write.csv(final_index, "daily_wire_extracted_articles.csv")
```

