---
title: "Daily Wire Scraper"
author: "Rob Wells and his pal Claude.ai"
date: "05-01-2025"
  output:
  html_document: default
  pdf_document: default
---

This notebook runs a Google power search query on a specific news site and then scrapes the results into individual text files into a separate folder. It compiles an index of the results with headline, date and URL.

It uses the Google Search API which is a rough way to extract article text from a website without the API access.

There are important limitations:

Google Search API limits results to 100 specific URLs at a time. 

For researchers seeking to several hundred or several thousand results, you can get around that by determining the result distribution and then breaking up the searches into blocks of 100 and compiling the results.

The first step is to use Google power search operators to find your material and validate the search results. We did this to get all Kamala Harris articles on the Daily Wire:

site:www.dailywire.com "kamala harris" after:2024-08-01 before:2024-08-10

Special thanks Nino Mtchedlisvili for her assistance on this project.


```{r}
# Install and load required packages if not already installed
#install.packages("rvest")
library(rvest)
library(tidyverse)
library(jsonlite)
library(httr)
#install.packages("googleAuthR")
library(googleAuthR)
library(lubridate)
```


# Set up API credentials
```{r}
# You'll need to get these from Google Cloud Console
# Visit: https://console.cloud.google.com/
# 1. Create a project
# 2. Enable Custom Search API
# 3. Create credentials
# 4. Set up a Custom Search Engine at https://programmablesearchengine.google.com/
```

# Important! DO NOT STORE YOUR API Key in GitHub!

```{r echo=FALSE}

Sys.setenv(GOOGLE_SEARCH_API_KEY = "XXX")
Sys.setenv(GOOGLE_SEARCH_ENGINE_ID = "XXX")


```

# Your credentials here
System environment variables exist at the operating system level, providing a more secure way to store sensitive information like API keys. They won't appear in your normal R environment but remain accessible across different sessions. You retrieve them using Sys.getenv(). These credentials typically persist only for the duration of your current R session.
```{r}

api_key <- Sys.getenv("GOOGLE_SEARCH_API_KEY")
search_engine_id  <- Sys.getenv("GOOGLE_SEARCH_ENGINE_ID")

```

# Count search results by date
### Define your search parameters
```{r}
# Define your parameters
site <- "www.dailywire.com"
search_term <- "kamala harris"

# Define date ranges to check (monthly intervals)
date_ranges <- list(
    c("2024-09-01", "2024-09-10"),
  c("2024-09-11", "2024-09-20"),
  c("2024-09-21", "2024-09-30")
)


  # c("2024-07-01", "2024-07-31"),
  # c("2024-08-01", "2024-08-31"),
  # c("2024-09-01", "2024-09-30"),
  # c("2024-10-01", "2024-10-31"),
  # c("2024-11-01", "2024-11-05")
# If you want to see how results are distributed within September
# september_ranges <- list(
#   c("2024-09-01", "2024-09-10"),
#   c("2024-09-11", "2024-09-20"),
#   c("2024-09-21", "2024-09-30")
# )

```


# Create the search function
```{r}
#New version specifies Google search in the US, use English and disables personalization of search results. All done for consistent results.
count_results_by_date <- function(api_key, search_engine_id, site, search_term, date_ranges) {
  #creates empty dataframe that stores search result counts
  results_count <- data.frame(
    date_range = character(),
    result_count = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (date_range in date_ranges) {
    # Building the search query
    query <- paste0('site:', site, ' "', search_term, '" after:', date_range[1], ' before:', date_range[2])
    
    # Make the API request
    response <- GET(
      "https://www.googleapis.com/customsearch/v1",
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = query,
        num = 1,  # requests only 1 result -only need the count, not actual results
        personalization = "false",  # Disable personalization
        gl = "us",                  # Set country to US
        hl = "en"                   # Set language to English
      )
    )
    
    # Parse the response
    # Checks if the API request was successful (status code 200)
    if (status_code(response) == 200) {
      results <- fromJSON(rawToChar(response$content))
      
      # Extracts the total result count 
      total_results <- as.numeric(results$searchInformation$totalResults)
      
      # Add to dataframe
      new_row <- data.frame(
        date_range = paste(date_range[1], "to", date_range[2]),
        result_count = total_results,
        stringsAsFactors = FALSE
      )
      
      results_count <- rbind(results_count, new_row)
      
      message("Query: ", query)
      message("Results: ", total_results)
    } else {
      message("Error for date range ", date_range[1], " to ", date_range[2], 
              ": Status code ", status_code(response))
    }
    
    # One second pause to avoid hitting rate limits with API query
    Sys.sleep(1.5)
  }
  #Returns the completed data frame containing all date ranges and their corresponding result counts
  return(results_count)
}


```

# Run the function, count monthly data
```{r}
monthly_counts <- count_results_by_date(api_key, search_engine_id, site, search_term, date_ranges) 
# View results
print(monthly_counts)
```

```{r}
get_results_with_urls <- function(api_key, search_engine_id, site, search_term, date_ranges) {
  library(httr)
  library(jsonlite)
  
  # Create a list to store results for each date range
  all_results <- list()
  
  for (i in seq_along(date_ranges)) {
    date_range <- date_ranges[i]
    
    # Format search query with date range
    query <- paste0(site, " ", search_term, " ", date_range)
    
    # Make API request to Google Search
    response <- GET(
      url = "https://www.googleapis.com/customsearch/v1",
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = query
      )
    )
    
    # Get the raw text response
    response_text <- content(response, "text", encoding = "UTF-8")
    
    # Parse JSON manually
    parsed_json <- fromJSON(response_text)
    
    # Extract count
    count <- 0
    if (!is.null(parsed_json$searchInformation$totalResults)) {
      count <- as.integer(parsed_json$searchInformation$totalResults)
    }
    
    # Create a result object for this date range
    result_obj <- list(
      date_range = date_range,
      count = count,
      items = list()
    )
    
    # Extract items if they exist
    if (count > 0 && !is.null(parsed_json$items)) {
      # Create simple data frame of search results
      items_df <- data.frame(
        title = character(),
        url = character(),
        snippet = character(),
        stringsAsFactors = FALSE
      )
      
      # Add each search result item to the data frame
      for (item in parsed_json$items) {
        item_title <- ifelse(is.null(item$title), NA_character_, item$title)
        item_url <- ifelse(is.null(item$link), NA_character_, item$link)
        item_snippet <- ifelse(is.null(item$snippet), NA_character_, item$snippet)
        
        # Add to data frame one row at a time
        items_df <- rbind(items_df, data.frame(
          title = item_title,
          url = item_url,
          snippet = item_snippet,
          stringsAsFactors = FALSE
        ))
      }
      
      result_obj$items <- items_df
    }
    
    # Store this result in our list
    all_results[[i]] <- result_obj
  }
  
  # Return the list of results
  return(all_results)
}

results <- get_results_with_urls(api_key, search_engine_id, site, search_term, date_ranges)
```

```{r}
# Print the search results in a readable format
print_search_results <- function(results) {
  for (i in seq_along(results)) {
    result <- results[[i]]
    
    cat("\n===== Date Range:", result$date_range, "=====\n")
    cat("Total Results:", result$count, "\n\n")
    
    if (length(result$items) > 0) {
      for (j in seq_along(result$items)) {
        item <- result$items[[j]]
        cat(j, ". ", item$title, "\n")
        cat("   URL: ", item$url, "\n")
        cat("   Snippet: ", item$snippet, "\n\n")
      }
    } else {
      cat("No search results found for this date range.\n\n")
    }
    
    cat("--------------------------------------\n")
  }
}
```




```{r}
# Convert results list to a data frame
results_to_dataframe <- function(results_list) {
  # Create empty data frame
  all_data <- data.frame(
    date_range = character(),
    count = integer(),
    url = character(),
    title = character(),
    snippet = character(),
    stringsAsFactors = FALSE
  )
  
  # Process each date range
  for (result in results_list) {
    # If there are URLs for this date range
    if (length(result$urls) > 0) {
      # Create a data frame for this date range's results
      date_df <- data.frame(
        date_range = rep(result$date_range, length(result$urls)),
        count = rep(result$count, length(result$urls)),
        url = result$urls,
        title = result$titles,
        snippet = result$snippets,
        stringsAsFactors = FALSE
      )
      
      # Append to overall data frame
      all_data <- rbind(all_data, date_df)
    } else {
      # Add a row with just the date range and count, but NA for URL info
      all_data <- rbind(all_data, data.frame(
        date_range = result$date_range,
        count = result$count,
        url = NA_character_,
        title = NA_character_,
        snippet = NA_character_,
        stringsAsFactors = FALSE
      ))
    }
  }
  
  return(all_data)
}


results_df <- results_to_dataframe(results)
```



# Graph monthly results

```{r}
library(ggplot2)
monthly_counts |> 
  mutate(month = case_when(
    str_detect(date_range, "2024-07-01") ~ "July",
    str_detect(date_range, "2024-08-01") ~ "Aug",
    str_detect(date_range, "2024-09-01") ~ "Sept",
    str_detect(date_range, "2024-10-01") ~ "Oct",
    str_detect(date_range, "2024-11-01") ~ "Nov",
    TRUE ~ date_range  # Default case to handle any unmatched values
  )) |> 
  mutate(month = factor(month, levels = c("July", "Aug", "Sept", "Oct", "Nov"))) |>
ggplot(aes(x = month, y = result_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(
    title = "DailyWire Articles Mentioning 'Kamala Harris' by Month",
    x = "Month",
    y = "Number of Articles"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    text = element_text(family = "sans"),
    plot.title = element_text(hjust = 0.5)
  )
```

# Query to fetch article URLs by date

### Specify search query parameters
```{r}
site <- "www.dailywire.com"
search_term <- "kamala harris"
#Dates
date_after <- "2024-09-01"
date_before <- "2024-09-10"
```


# Search query to extract the URLS

```{r}
google_search_all <- function(api_key, search_engine_id) {
  base_url <- "https://www.googleapis.com/customsearch/v1"
  all_results <- data.frame(
    url = character(),
    title = character(),
    snippet = character(),
    stringsAsFactors = FALSE
  )
  

  
  # Google only allows up to 100 pages 
  for(start_index in seq(1, 300, 10)) {
     # Building the search query
    query <- paste0('site:', site, ' "', search_term, '" after:', date_after, ' before:', date_before)
    
    # Add delay to avoid hitting rate limits
    Sys.sleep(1)
    
    response <- GET(
      base_url,
      query = list(
        key = api_key,
        cx = search_engine_id,
        q = query,
        start = start_index,
        personalization = "false",  # Disable personalization
        gl = "us",                  # Set country to US
        hl = "en"                   # Set language to English
      )
    )
    
    results <- fromJSON(rawToChar(response$content))
    
    # Check if we have items in the response
    if(!is.null(results$items)) {
      page_df <- data.frame(
        url = results$items$link,
        title = results$items$title,
        snippet = results$items$snippet,
        stringsAsFactors = FALSE
      )
      
      all_results <- rbind(all_results, page_df)
      
      # Print progress
      cat("Retrieved results", start_index, "to", start_index + nrow(page_df) - 1, "\n")
    } else {
      # If no more results, break the loop
      break
    }
        # One second pause to avoid hitting rate limits with API query
    Sys.sleep(2.5)
  }
  
  return(all_results)
}

# Get all results
all_urls_df <- google_search_all(api_key, search_engine_id)
# Remove any duplicates
clean_urls_df <- unique(all_urls_df)
# Print total number of results
cat("\nTotal unique articles found:", nrow(clean_urls_df), "\n")
```


#-------------------------------------------------------------------------------
# Part 2 : Scraping the text
#-------------------------------------------------------------------------------


#I asked ChatGPT:  build a webscraper this into a function so it will extract URLs from Daily_Wire_Articles.xlsx from the URL column and produce one text file per article. there are 20 URLs on that list.

```{r}
# Define the function to scrape a Daily Wire article
scrape_article <- function(url) {
  # Read the HTML content of the page
  page <- tryCatch(
    read_html(url),
    error = function(e) {
      message(paste("Error reading:", url))
      return(NULL)
    }
  )
  
  # Return NULL if page could not be loaded
  if (is.null(page)) return(NULL)

  # Extract the headline (assuming it's in an <h1> tag)
  headline <- page %>%
    html_element("h1") %>%
    html_text(trim = TRUE)

  # Extract the article text (all <p> elements)
  article_text <- page %>%
    html_elements("p") %>%
    html_text(trim = TRUE) %>%
    paste(collapse = "\n")

  # Combine headline and article into one string
  full_text <- paste("Headline:\n", headline, "\n\nArticle Text:\n", article_text)
  
  return(full_text)
}

# Read the URLs from the Excel file
# You will need to point to the location of your Daily Wire Articles spreadsheet.
# urls <- read_excel("~/Code/CompText_Jour/data/Daily_Wire_Articles.xlsx", sheet = 1)$URL

urls <- clean_urls_df$url
# Create directory if it doesn't exist
dir.create("extracted_articles", showWarnings = FALSE)

# Loop over URLs and save each article as a text file
for (url in urls) {
  article_content <- scrape_article(url)
  
  # Skip if article content is NULL
  if (is.null(article_content)) next
  
  # Create a filename from the URL (using only the last part)
  filename <- paste0(basename(url), ".txt")
  
  # Create the full path including the new directory
  filepath <- file.path("extracted_articles", filename)
  
  # Save the article content to a text file in the new directory
  writeLines(article_content, con = filepath)
  
  message(paste("Saved:", filepath))
}

```

#Create a final index

```{r}
#add the url_df here
final_index <- rbind(august_10_urls_df, sept_urls_df) |> 
  # Extract date pattern from snippet column
  mutate(date_str = str_extract(snippet, "[A-Z][a-z]{2}\\s+\\d{1,2},\\s+\\d{4}")) %>%
  # Convert extracted strings to Date objects
  mutate(date = mdy(date_str)) %>%
  # Remove the intermediate string column if you don't need it
  select(-date_str)


write.csv(final_index, "daily_wire_extracted_articles.csv")
```

